\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}

### 2013-12-16 docs/paper/paper.tex
Removed merge errors from document. Why on earth would you push conflicts? O.o

\subsection{Causal inference}
An approach for finding effective connectivity may be found in the domain of causal discovery.
A causal discovery method uses data about events to determine which of these events are correlated, and additionally, it attempts to determine which events cause which.
The definition of a causal relation is not trivial \cite[p.20]{spirtes2000} and the relevant principles will be covered in this section.
In our context, the causal discovery methods which have been used aim at inferring a Directed Acyclic Graph (DAG).
These can be interpreted from a probabilistic and a causal perspective.
%In our case, we consider graphs that also include non-directed edges, a so called Partial DAG (PDAG).

@@

The results from the altorithms are presented in the form of matrices.
A connection from region $n$ to region $m$ is represented by point $(n,m)$ or $n,m$ in the matrix.
For strucural data, this matrix is therefore symmetrical.
In the directional data, point $(n,m)$ denotes a directed edge from $n$ to $m$.
In such a matrix, indices 1-45 represent the brain regions of the left hemisphere, regions 45-90 represent the right hemisphere, and regions 91-116 represent regions in the cerebellum. %TODO left or right hemisphere?
Modified PC and EMS-PC do not differ in finding the structure.
The results are presented in figure ~\ref{fig:struct_avg} as the avarage over all six subjects, with 300 iterations per subject. Additionaly, separate parts of the two hemispheres, the inter-hemisphere, and the cerebellum are presented in Figure ~\ref{fig:struct_apart}
The results of Hinne et al. are shown as well for comparison.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{images/struct_full}
  \includegraphics[width=0.5\textwidth]{images/structure_max}
  \caption{The avarage structure of all subjects. The first structure is found with the PC-algorithm, and the second structure is found by Hinne et al.}
  \label{fig:struct_avg}
\end{figure}
In this matrix, higher values represent strong certainties of the presence of a connection.

>>>>

\subsection{Causal Discovery}
An approach for finding effective connectivity may be found in the domain of causal discovery.
A causal discovery method uses data about events to determine which of these events are correlated, and additionally, it attempts to determine which events cause which.
The definition of a causal relation is not trivial \cite[p.20]{spirtes2000} and the relevant principles will be covered in this section.
In our context, the causal discovery methods which have been used aim at inferring a Directed Acyclic Graph (DAG).
These can be interpreted from a probabilistic and a causal perspective.
%In our case, we consider graphs that also include non-directed edges, a so called Partial DAG (PDAG).

@@

The results from the altorithms are presented in the form of matrices.
A connection from region $n$ to region $m$ is represented by point $(n,m)$ or $n,m$ in the matrix.
For strucural data, this matrix is therefore symmetrical.
In the directional data, point $(n,m)$ denotes a directed edge from $n$ to $m$.
In such a matrix, indices 1-45 represent the brain regions of the left hemisphere, regions 45-90 represent the right hemisphere, and regions 91-116 represent regions in the cerebellum. %TODO left or right hemisphere?
Modified PC and EMS-PC do not differ in finding the structure.
The results are presented in figure ~\ref{fig:struct_avg} as the avarage over all six subjects, with 300 iterations per subject. Additionaly, separate parts of the two hemispheres, the inter-hemisphere, and the cerebellum are presented in Figures \ref{fig:struct_left}, \ref{fig:struct_right}, \ref{fig:struct_inter_hemisphere}, \ref{fig:struct_cerebellum}, \ref{fig:struct_apart}
The results of Hinne et al. are shown as well for comparison.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{images/struct_full}
  \includegraphics[width=0.5\textwidth]{images/structure_max}
  \caption{The avarage structure of all subjects. The structure on the left is found with the PC-algorithm, and the structure on the right is found by Hinne et al.}
\label{fig:struct_avg}
\end{figure}
In this matrix, higher values represent strong certainties of the presence of a connection.
